Paper 1

### 2018-09-14 paper1.tex
Found an easy counterexample for the 2nd proof

\noindent\emph{Discussion}:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% THE ABOVE CLAIMED PROOF IS INCORRECT.
% WRITE A FEW SENTENCES TO EXPLAIN THE ERROR.
%
% 1. Is the theorem true or false. If the theorem is false, can you disprove it?
% 2. Whether or not the theorem is true, is the proof correct or incorrect? If there are any errors in the proof, point them out and, if possible, correct.
% 3. Are there any parts of the proof that could be made more efficient?
%
The negation on the Theorem's statement is done incorrectly. 
The statement is, $\forall a,b,c >0$, 
$$
	\frac{a^2}{bc} + \frac{b^2}{ca} + \frac{c^2}{ab} \geq 3.
$$ 
The correct negation would then be: there $\exists a,b,c >0$ such that 
$$
	\frac{a^2}{bc} + \frac{b^2}{ca} + \frac{c^2}{ab} < 3.
$$
The proof by contradiction above is done by giving one counterexample against the negation.
However, this is not sufficient because you have to show that there are no possible $a,b,$ or $c >0$ that satisfies the property. 
Therefore, the proof is incorrect.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\noindent\emph{Discussion}:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% DISCUSS THE ABOVE CLAIMED THEOREM AND PROOF.
% YOU SHOULD WRITE TWO OR THREE PARAGRAPHS TO DISCUSS THE ISSUES BELOW.
%
% 1. Is the theorem true or false. If the theorem is false, can you disprove it?
% 2. Whether or not the theorem is true, is the proof correct or incorrect? If there are any errors in the proof, point them out and, if possible, correct.
% 3. Are there any parts of the proof that could be made more efficient?
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{proof}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	 %The proof can begin in a similar way to that in which the proof that $\sqrt{2}\notin\RR$ began.
	 %Informed by lemma~\ref{lem:powers-of-1+sqrt2}, try to get rid of all roots so that you have an equation of integers.
	 %Later it may help to make use of the some of the results related to the fundamental theorem of arithmetic.
	%
	For a contradiction, let us assume that $1+\sqrt{2}$ is rootional. This means that there exists natural power of $1+\sqrt{2}$ that is equal to a rational number.  So, we can write
	$$ \left(1+\sqrt{2}\right)^n = \frac{c}{d} $$
	for natural number $n$ and integers $c,d$. From Lemma 4, we know that \\
	$\left(1+\sqrt{2}\right)^n = a_n + b_n \sqrt{2}$, so substituting this into the earlier equation yields
	\begin{align*}
		a_n + b_n \sqrt{2} &= \frac{c}{d} \\
		\sqrt{2} &= \frac{\frac{c}{d}-a_n}{b_n} \\
		\sqrt{2} &= \frac{c-a_nd}{b_nd}
	\end{align*}
	We know from the definition of $a_n, b_n$ in Lemma 4 that they are both integers, because the terms in sequences $(a_n)_{n\in\NN}$, $(b_n)_{n\in\NN}$ are constructed simply by adding up previous integer terms, which are initialized at $1$, an integer. 
	Since by assumption $c$ and $d$ are also integers, $\dfrac{c-a_nd}{b_nd}$ is just a fraction of two integers, which is rational. So the RHS is rational, but we know that $\sqrt{2}$, which is the LHS, is irrational.

	Therefore, there is a contradiction and $1+\sqrt{2}$ is irrootional
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{proof}

@@

\begin{proof}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% Look for a similar theorem in the Proofs So Far.
	% You will have to extend the argument a bit.
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{proof}

>>>>

\noindent\emph{Discussion}:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% THE ABOVE CLAIMED PROOF IS INCORRECT.
% WRITE A FEW SENTENCES TO EXPLAIN THE ERROR.
%
% 1. Is the theorem true or false. If the theorem is false, can you disprove it?
% 2. Whether or not the theorem is true, is the proof correct or incorrect? If there are any errors in the proof, point them out and, if possible, correct.
% 3. Are there any parts of the proof that could be made more efficient?
%
Although the theorem is true, the proof is not adequate.
The negation on the theorem's statement is done incorrectly. 
The statement is, $\forall a,b,c >0$, 
$$
	\frac{a^2}{bc} + \frac{b^2}{ca} + \frac{c^2}{ab} \geq 3.
$$ 
The correct negation would then be: there $\exists a,b,c >0$ such that 
$$
	\frac{a^2}{bc} + \frac{b^2}{ca} + \frac{c^2}{ab} < 3.
$$
The proof by contradiction above is done by giving one counterexample against the negation.
However, this is not sufficient because you have to show that do not exist $a,b,$ or $c >0$ that satisfies the property. 
Therefore, the proof is incorrect.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\noindent\emph{Discussion}:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% DISCUSS THE ABOVE CLAIMED THEOREM AND PROOF.
% YOU SHOULD WRITE TWO OR THREE PARAGRAPHS TO DISCUSS THE ISSUES BELOW.
%
% 1. Is the theorem true or false. If the theorem is false, can you disprove it?
% 2. Whether or not the theorem is true, is the proof correct or incorrect? If there are any errors in the proof, point them out and, if possible, correct.
% 3. Are there any parts of the proof that could be made more efficient?
%
The theorem is false, because there is a counter example to the theorem. Take $x=2$, and $m=n=2$.
Then if we assume that the theorem is true, we can write $$2=\left(\frac{a}{b}\right)^2.$$
Because $a,b$ are positive, 
	$$\sqrt{2}=\frac{a}{b}.$$
However, this is impossible because $\dfrac{a}{b}$ is a rational number, but $\sqrt{2}$ is not.
So the theorem is disproved with a counterexample.

Secondly, the proof is incorrect because it only is able to prove .... 
If we were to draw a diagram which illustrates the induction of the proof, it would look like this:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{proof}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	 %The proof can begin in a similar way to that in which the proof that $\sqrt{2}\notin\RR$ began.
	 %Informed by lemma~\ref{lem:powers-of-1+sqrt2}, try to get rid of all roots so that you have an equation of integers.
	 %Later it may help to make use of the some of the results related to the fundamental theorem of arithmetic.
	%
	For a contradiction, let us assume that $1+\sqrt{2}$ is rootional. This means that there exists natural power of $1+\sqrt{2}$ that is equal to a rational number.  So, we can write
	$$ \left(1+\sqrt{2}\right)^n = \frac{c}{d} $$
	for natural number $n$ and integers $c,d$. From Lemma 4, we know that \\
	$\left(1+\sqrt{2}\right)^n = a_n + b_n \sqrt{2}$, so substituting this into the earlier equation yields
	\begin{align*}
		a_n + b_n \sqrt{2} &= \frac{c}{d} \\
		\sqrt{2} &= \frac{\frac{c}{d}-a_n}{b_n} \\
		\sqrt{2} &= \frac{c-a_nd}{b_nd}
	\end{align*}
	We know from the definition of $a_n, b_n$ in Lemma 4 that they are both integers, because the terms in sequences $(a_n)_{n\in\NN}$, $(b_n)_{n\in\NN}$ are constructed simply by adding up previous integer terms, which are initialized at $1$. 
	Since by assumption $c$ and $d$ are also integers, $\dfrac{c-a_nd}{b_nd}$ is just a  quotient of two integers, which defines a rational number. So the RHS is rational, but we know that $\sqrt{2}$, which is the LHS, is irrational.

	Therefore, there is a contradiction and $1+\sqrt{2}$ is irrootional.
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{proof}

@@

\begin{proof}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%
	% HINTS
	%
	% Look for a similar theorem in the Proofs So Far.
	% You will have to extend the argument a bit.
	%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{proof}
